The Name of the Title is Hope

### 2020-03-19 discussion.tex
Clean up task 2 stuff

\subsection{Statistical insignificance}
Why it be like it do?

\subsection{Task 2}
The Wilcoxon Rank-Sum test on task 2 was $p=0.03$, showing a runaway success
that examples do help participants find the correct program faster.
%
We suspect that second task was unique among the four participants completed.
%
The tool produced up to ten candidate programs for a given type signature, and
for task 2, the correct solution was at the very end.
%
Task 1 and 4 had the correct solution listed in the first and second places,
respectively.

>>>>

\subsection{Hope for examples}
Although the study failed to show that examples aided candidate selection in
the general case, it's possible that in specific case it makes a large difference.
%
A Wilcoxon Rank-Sum test on the data from Task 2 shows that the \example
group was faster with a confidence of $p=0.03$.
%
While this could just be noise, the correct solution for Task 2 was 10th in
the list while Tasks 1 and 2 had their solution in the first two spots.
%
Task 3 had no solution.
%
If examples speed up candidate assessment, we'd expect this effect to be
magnified by the number of candidates assessed.
%
Because users had to sift through 9 incorrect solutions to get to the correct
one, it makes sense that Task 2 showed the most dramatic effect.
%
A study that randomizes solution location rather than preserving the synthesizer's ordering
could test this hypothesis.
